Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-07 Paper.tex
Intro shortened

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage{hyperref}

@@

\name{Peter Naylor$^{1,2,3}$\sthanks{Peter Naylor has received a PhD
  fellowship from the Ligue contre le Cancer. } \qquad Marick La\'e$^{4}$
  \qquad Fabien Reyal$^{2}$\qquad Thomas Walter$^{1,2,3}$}

\address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
  de Bioinformatique,\\ 
  35 rue St Honoré 77300 Fontainebleau, France \\
$^{2}$Institut Curie, 75248 Paris Cedex, France\\
$^{3}$INSERM U900, 75248 Paris Cedex, France\\
$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
%The abstract should appear at the top of the left-hand column of text, about
%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
%beginning of the main text.  The abstract should contain about 100 to 150
%words, and should be identical to the abstract text submitted electronically
%along with the paper cover sheet.  All manuscripts must be in English, printed
%in black ink.
\end{abstract}
%
\begin{keywords}
Deep Learnnig, Convolutional Neural Networks, Nuclei Segmentation,
Histpathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

% images in cancer research, histopathology --> digital pathology
\noindent Today, large sequencing approaches build the main body of cancer
research programs and they have revolutionized our understanding of
the molecular basis of cancer. In clinical practice however,
molecular profiling is paralleled with the more traditional
(and mostly manual) analysis of stained histological tumor
sections. With the avent of digital pathology, i.e. the scanning and
digital storage of diseased tissue sections, it is now possible to
build tools for the quantitative and automatic analysis of these
complex and informative image data. Indeed, this is a very promising
approach for several reasons: image based approaches
provide us with spatial information that is absent in genomic,
transcriptomic and epigenetic studies of cancer. In addition they
allow analysis of individual cells, such that it is possible to study
cellular heterogeneity. Cellular heterogeneity has been acknowledged
to be of major importance in cancer research and treatment. Also, it
is possible to analyze cells in terms of morphology and phenotype,
which brings in a complementary piece of functionally relevant
information.

>>>>

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage{hyperref}
\usepackage{seqsplit}

@@

\name{Peter Naylor$^{1,2,3}$\sthanks{Peter Naylor has received a PhD
  fellowship from the Ligue contre le Cancer} \qquad Marick La\'e$^{4}$
  \qquad Fabien Reyal$^{5,6,7}$\qquad Thomas Walter$^{1,2,3}$}

\address{\normalsize $^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
  de Bioinformatique, 77300 Fontainebleau, France;\\
\normalsize $\quad ^{2}$Institut Curie,  
$\quad ^{3}$INSERM U900, Paris, 
$\quad ^{4}$Service de Pathologie, Institut Curie, Paris, F-75248, France\\
\normalsize $\quad ^{5}$Residual Tumor \& Response to Treatment Laboratory,
RT2Lab, Translational Research Department, Institut Curie, \\
\normalsize $\quad ^{6}$U932, Immunity and Cancer, INSERM, Institut Curie, 
$\quad ^{7}$Department of Surgery, Institut Curie, Paris, F-75248, France.
}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Analysis and interpretation of stained tumor sections is one of the
main tools in cancer diagnosis and prognosis, which is mainly carried
out manually by pathologists. The avent of digital pathology provides
us with the challenging opportunity to automatically analyze large
amounts of these complex image data in order to draw
biological conclusions from them and to study cellular and tissular
phenotypes at a large scale. One of the bottlenecks for such
approaches is the automatic segmentation of cell nuclei from this type
of image data. Here, we present a fully automated workflow to segment
nuclei from histopathology image data by using deep neural
networks trained from a set of manually annotated images and by processing
the posterior probability maps in order to split jointly segmented
nuclei. Further, we provide the image data set that has been generated
for this study as a benchmark set to the scientific community.  
\end{abstract}
%
\begin{keywords}
Deep Learning, Convolutional Neural Networks, Nuclei Segmentation,
Histopathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

% images in cancer research, histopathology --> digital pathology
Today, large sequencing approaches build the main body of cancer
research programs and they have revolutionized our understanding of
the molecular basis of cancer. In clinical practice however,
molecular profiling is paralleled with the more traditional
(and mostly manual) analysis of stained histological tumor
sections. With the avent of digital pathology, i.e. the scanning and
digital storage of diseased tissue sections, it is now possible to
build tools for the quantitative and automatic analysis of these
complex and informative image data. These image data are in many ways
complementary to genomic and expression data, as they are informative
about the spatial dimension, they allow one to assess cellular
heterogeneity and allow for single cell analysis in terms of
morphology and phenotype.
